\documentclass{article}
\usepackage{blindtext}
\title{How to solve a Rubik's cube}
\author{John Gould}
\begin{document}
    \maketitle
    \begin{enumerate}
        \item \textbf{Construct the daisy}

              Find the yellow centre and surround it with with four white edges.
        \item \textbf{Create a white cross}

              Match other square on white edge with same coloured centre square on its face.
              Rotate the face 2. Repeat for other `daisy petals'.
        \item \textbf{Get whites on to the bottom layer}
        
              Turn white square onto bottom. Find white squares on top layer (not top face).
              Turn top layer such that square adjacent to white square (same cube but not top face)
              is diagonal to centre square of same colour. Perform right/left trigger accordingly.
              If a white is on bottom layer, right/left trigger it to top layer. If white on top, rotate
              top layer such that white square is above non-white square on bottom face. Now perform right/left
              trigger twice to get it onto top row (not face). Repeat until bottom face is all white. Bottom 
              row will also be solved.
        \item \textbf{Solve the second layer}

              Find edge piece on top layer that do NOT contain yellow. Create `T' on one face.
              Look to see if top face colour above `T' is matched with centre square on left or right face.
              Pull top layer once with right(left) index finger if match is on right(left) then perform right(left)
              trigger. Reposition displace white square as before. Continue until second layer is solved.

        \item Create a yellow cross
        \item Solve the yellow face
        \item $L'\quad
               U\quad
               R\quad
               U'\quad
               L\quad
               U2\quad
               R'\quad
               U\quad
               R\quad
               U2\quad
               R'$
        \item Finish the cube
    \end{enumerate}
\end{document}